EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-12 draft.tex
REvised cloud deployment section

Container-based applications describe the deployment of isolated processes in a
consistent and portable way, going from development, testing, and production
independently on the kind of infrastructure. The term cloud-native describes
these container-based environments because they are deployed on an
infrastructure that abstracts the underlying compute, storage, and networking
primitives. This infrastructure does need to be a cloud provider; it could be a
developer's laptop, a single server, or a production environment. When we deploy
a cloud-native application to a cloud provider, we have more options to choose:

@@

As a proof-of-concept, we chose the third option and deployed the EvoSwarm application in Amazon Elastic
Container Service (ECS),  since it needs fewer changes in configuration 
(from deploying it locally using docker-compose) and it is has a lower cost than a Kubernetes alternative.

We can define an ECS cluster directly on AWS Elastic Cloud VMs or through AWS Fargate.
Fargate is a serverless compute engine for containers that provides automatic provision 
and management of AWS ECS resources. With this service, calculating the cost of execution
is simplified because users only specify the computing units and memory for all the application,
instead of every component.

Multicontainer applications are 
% Maybe an example - JJ
% This is shown next - Mario
deployed to ECS as tasks, and a single cluster can run multiple tasks in
parallel. When using the Fargate service as a backend, tasks are limited to a
maximum of 10 containers.

Using the ECS CLI, we can provision a cluster with a configuration file
specifying the computing resources needed. We can specify the configuration a Task 
by using a task definition file (see Listing~\ref{code:ecs}) in YAML format.
The main attributes are the {\texttt task\_size} indicating the memory and CPU units
assigned, and network configuration. The complete configuration of the task is generated
by the {\texttt compose command} that uses a {\texttt docker-compose.yml} to generate 
the configuration on-the-fly. For example to deployed the controller, setup and redis 
containers we used the file in Listing ~\ref{code:compose}.

@@

For the second option we assigned each worker to a single task with 4GBs of memory and 2048 computing units,
and scale the number of worker Tasks to eight.

@@

The results are shown in Table X.

>>>>

Container-based applications describe the deployment of loosely coupled processes in a
consistent and portable way, in every phase of the life cycle of an application, from development through testing to production
independently on the kind of infrastructure. The term cloud-native describes
these container-based environments because they are deployed on an
infrastructure that abstracts the underlying compute, storage, and networking
primitives. This infrastructure does need to be a cloud provider; it could be a
developer's laptop, a single server, or a production environment. When we deploy
a cloud-native application to a cloud provider, we have some more options to choose:

@@

As a proof-of-concept, we chose the third option and deployed the EvoSwarm application in Amazon Elastic
Container Service (ECS),  since it needs fewer changes in configuration 
(from deploying it locally using docker-compose) and it is has a lower cost than the Kubernetes alternative. % Remember to mention cost at the end - JJ

We can define an ECS cluster directly on AWS Elastic Cloud VMs or through the AWS Fargate service.
Fargate is a serverless compute engine for containers that provides automatic provision 
and management of AWS ECS resources. With this service, calculating the cost of execution
is simplified because users only specify the computing units and memory for all the application,
instead of every component.

Multicontainer applications are deployed to ECS as tasks, and a single cluster can run multiple tasks in
parallel. When using the Fargate service as a backend, tasks are limited to a
maximum of 10 containers.

Using the ECS CLI, we can provision a cluster with a configuration file
specifying the computing resources needed. We can specify the configuration of a Task 
by using a task definition file (see Listing~\ref{code:ecs}) in YAML format.
The main attributes are the {\texttt task\_size} indicating the memory and CPU units
assigned, and network configuration. The complete configuration of the task is generated
by the {\texttt compose command} that uses a {\texttt docker-compose.yml} file to generate 
the configuration on-the-fly. For example to deployed the controller, setup and redis 
containers we used the file in Listing ~\ref{code:compose}.

@@

For the second option we assigned each worker to a single task with 4GBs of memory and 2048 computing units,
and scale the number of worker tasks to eight.  % Please use caps or not for Tasks in a consistent way - JJ

@@

% Please clarify that those images are published in Docker hub by yourself - JJ
The results are shown in Table X.
